---
title: "exploring_protest_type"
output: 
      pdf_document: default
      html_document:
        df_print: paged
Name: Manasvi Khanna
---

```{r}
rm(list = ls())
```



```{r}
getwd() # set working directory 
dir <- "/Users/manasvikhanna/Desktop/Farmer's Protest/farmers_protest_git"
setwd(dir)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
```{r}
library(dplyr)
library(tidyr)
library(ggmap)
library(spatstat)
library(tigris)
library(spdep)
library(ggplot2)
library(broom)
library(sp)
library(raster)
library(tidycensus)
library(maditr)
library(gridExtra)
```

```{r}
allProtests <- read.csv("data/original/Farmer_s Protest Data.csv") # read data
colnames(allProtests)
table(allProtests$year) # check which years are represented in the data 
```

```{r}
# since we only need the protests that happened after the new laws
farmers_protest <- filter(allProtests,year >2018) 
table(farmers_protest$year)
```

```{r}
# reading a shape of India that has data at state level 
state_shape <- rgdal::readOGR(dsn = "/Users/manasvikhanna/Desktop/Farmer's Protest/shape_files/maps-f0f120311fefd5049b0dab6856c2fa5bf06e9b08/States",
                               layer= "Admin2")
```
```{r}
# This is the data saved from Loading Data Sets with out demographic controls 
demographic_date <- read.csv("data/working/demographic_data.csv")
```

```{r}
# transform shapefile to standard projections 
state_shape <- spTransform(state_shape, CRS("+init=epsg:24370"))
```

```{r}
copyFarmer <- farmers_protest
coordinates(copyFarmer) <- ~longitude+latitude 
class(copyFarmer)
```

```{r}
# set cooridates on the farmers protest to match shape file

proj4string(copyFarmer) <- "+proj=longlat +datum=WGS84 +no_defs"
copyFarmer <- spTransform(copyFarmer, CRS("+init=epsg:24370"))
```

```{r}
# check if projections mathc 
c(proj4string(copyFarmer), proj4string(state_shape))
```

```{r}
in_fortify <- broom::tidy(state_shape)
```

```{r}
state_shape$id <- row.names(state_shape)
in_fortify <- left_join(in_fortify, state_shape@data)
```
```{r}
# Join shape file with demographic data 
state_shape@data <- left_join(state_shape@data, demographic_date, by = c("ST_NM" = "ST_NM"))

```

```{r}
# classify peaceful vs non peaceful into subsets for modelling comparisons

sub1 <- copyFarmer[copyFarmer$sub_event_type == "Peaceful protest",]
sub2 <- copyFarmer[copyFarmer$sub_event_type != "Peaceful protest",]
nrow(sub2)
```

```{r}
ind_poly <- as(state_shape, "SpatialPolygons")
ind_poly <- spTransform(ind_poly, CRS("+init=epsg:24370")) #project them
```

```{r}
ind_one <- st_transform(st_union(st_as_sf(ind_poly)), crs = CRS("+init=epsg:24370")) #comb
```

```{r}
ind_win <- as.owin(as_Spatial(ind_one)) #transform into window
```

```{r}
#coordinates(sub1) <- ~longitude+latitude
proj4string(sub1) <- proj4string(state_shape)
# reproject to match window
sub1 <- spTransform(sub1, CRS("+init=epsg:24370"))
sub2 <- spTransform(sub2, CRS("+init=epsg:24370"))
```


```{r}
over_dat1 <- over(sub1, ind_poly)
over_dat2 <- over(sub2, ind_poly)
length(which(is.na(over_dat2))) #0: they are all in the window
```


```{r}
# use the ppp (possion point process model) to calculate intensity 
sub1_ppp <- as.ppp(sub1@coords, W = ind_win)
plot(sub1_ppp)
```
```{r}
# use the ppp (possion point process model) to calculate intensity 

sub2_ppp <- as.ppp(sub2@coords, W = ind_win)
plot(sub2_ppp)
```
```{r}
# Use the density funciton to get density from the ppp model 
kernel_density1 <- density(sub1_ppp)
plot(kernel_density1, main = "KDE: Protest Type: Peaceful")
plot(sub1_ppp, add = T)
```

```{r}
kernel_density2 <- density(sub2_ppp)
plot(kernel_density2, main = "KDE: Protest Type: Not Peaceful")
plot(sub2_ppp, add = T)
```

```{r}
ppm(sub1_ppp, ~1)
ppm(sub2_ppp, ~1)
```


```{r}
# rescale to control for really high valeus
sub1rescaled <- rescale(sub1_ppp, 100000)
sub2rescaled <- rescale(sub2_ppp, 100000)
```

```{r}
# fit rescaled subsets to point process model with a linear trend in coordinates

fit1 <- ppm(Q = sub1rescaled, trend = ~x + y)
summary(fit1)
plot(fit1, main = "Protest Type: Not Peaceful")

```
```{r}
fit2 <- ppm(Q = sub2rescaled, trend = ~x + y)
summary(fit2)
plot(fit2)
```

```{r}

lattice <- expand.grid(Long = seq(state_shape@bbox[1,1],
                                  state_shape@bbox[1,2],length.out = 100), 
                       Lat = seq(state_shape@bbox[2,1],
                                 state_shape@bbox[2,2],length.out = 100))
dim(lattice)
plot(lattice)
```

```{r}
sp_lattice <- lattice
coordinates(sp_lattice) <- ~ Long+Lat
proj4string(sp_lattice) <- proj4string(state_shape)
overlap_set <- over(sp_lattice, state_shape)
```


```{r}
lattice <- lattice[!(is.na(overlap_set$ST_NM)),]
plot(lattice)
```
